\documentclass [11pt]{article}
%\nofiles

\pagestyle{plain}

\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}

%%%%%%%%%% EXACT 1in MARGINS %%%%%%% 
\setlength{\textwidth}{6.5in}     
\setlength{\oddsidemargin}{0in}   
\setlength{\evensidemargin}{0in}  
\setlength{\textheight}{8.5in}   
\setlength{\topmargin}{0in}    
\setlength{\headheight}{0in}    
\setlength{\headsep}{0in}         
\setlength{\footskip}{.5in}   

\begin{document}
%%%%%%%%% BIOGRAPHICAL SKETCH -- 2 pages/PI
\setlength{\baselineskip}{12pt}
\newpage
\setcounter{page}{1}
\parindent 0in
\begin{center}
{\Large\bf{\sc Biographical Sketch}}
\end{center}
\vspace*{-0.1in}
{\textcolor{black}{\makebox[6.5in]{\hrulefill}} ~\\
\vspace*{-0.35in}
\begin{tabbing}
   {\bf NAME} \hspace*{2.5in} \= {\bf POSITION TITLE} \\
   Christopher C. Lamb	      \>  Principal Member of Technical Staff, \\
                                                     \> Sandia National Laboratories
\end{tabbing}
\vspace*{-0.1in}
{\textcolor{black}{\makebox[6.5in]{\hrulefill}} ~\\
\vspace*{-0.2in}
\underline{\bf EMPLOYMENT:} ~\\
\begin{itemize}
\item October 2008 -- present: Principal Member of Technical Staff, Sandia National Laboratories
\item October 2005 -- October 2008: Limited Term Employee, Sandia National Laboratories
\item March 2004 -- October 2005: Engineering Consultant VI, Respec
\item March 2001 -- March 2004: Vice President, Software Engineering, Oso Grande Technologies
\item April 2000 -- March 2001: Senior Software Engineer, Earthscan Network
\item April 1999 -- April 2000: Software Engineer, Tally Systems Corporation
\item April 1995 -- April 1999: Systems Administrator, Maxwell Laboratories
\end{itemize}
\vspace*{-0.1in}
{\textcolor{black}{\makebox[6.5in]{\hrulefill}} ~\\

\vspace*{-0.2in}
\underline{\bf EDUCATION:} ~\\
\begin{tabular}{lccc}
{\bf INSTITUTION}  & {\bf DEGREE} & {\bf  FIELD OF} \\ 
                                                     && {\bf STUDY} \\
University of New Mexico & Ph.D. (Pending) & Computer Engineering \\
University of New Mexico & M.S. & Computer Science \\
New Mexico State University & B.S. & Mechanical Engineering \\~\\
\end{tabular}

{\textcolor{black}{\makebox[6.5in]{\hrulefill}} ~\\

{\bf A. \  \ \underline{RECENT PUBLICATIONS:}}
\begin{enumerate}
\item
C.~C. Lamb, P.~A. Jamkhedkar, G.~L. Heileman and C.~T. Abdallah. Managed Control of Composite Cloud Systems. {\sl 6th IEEE International Conference on 
System of Systems Engineering (SoSE)}, June 27--30, Albuquerque, NM (submitted).

\item 
C.~C. Lamb, P.~A. Jamkhedkar, G.~L. Heileman, R.~K. Kadaboina.  Usage Management of Personal Medical Records.  {\sl First IEEE Conference on Healthcare Informatics, Imaging, and Systems Biology (HISB)}. July 27--29, San Jose, CA (submitted).
 
\item
P.~A. Jamkhedkar, C. C. Lamb and G.~L. Heileman. Usage Mangement in Cloud Computing, {\sl Cloud 2011: IEEE International Conference on Cloud Computing}, Washington, DC, Jul 5--10, 2011 (to appear).

\item P. ~A. Jamkhedkar, G. ~L. Heileman and C. ~C. Lamb. An Interoperable Usage Management Framework. {\sl Proceedings of the Tenth ACM Workshop on Digital Rights Management}, ACM Conference on Computers and Communications Security, Chicago, IL, Oct. 4, 2010.
\end{enumerate} 

{\textcolor{black}{\makebox[6.5in]{\hrulefill}} ~\\


\underline{\bf TECHNOLOGIES:} ~\\
\textbf{Languages}: Scala, Clojure, Java, Ruby, C, C++, C\#, Erlang \\
\textbf{Frameworks}: Ruby on Rails, Java EE/SE/ME, JFace/SWT, .Net, ASP.Net MVC, Microchip MPLab Compilers \\
\textbf{Environments}: Eclipse, Netbeans, Visual Studio .Net, Microchip MPLab \\
\textbf{Modeling}: Rational Tools, MagicDraw UML, Visual Paradigm for UML, Poseidon for UML

\vspace*{0.2in}
\underline{\bf INTERESTS:} ~\\
Intelligent Agents, Rights Management, Software Architecture, Software Engineering, Distributed Computing, Cloud Computing

\vspace*{0.2in}
\underline{\bf HONORS:} ~\\
NNSA Defense Program Award of Excellence – 2005 \\ 
Sandia National Laboratories Quarterly SAFE award recipient – Fall, 1997 \\
NMSU Presidential Scholar \\
Crimson Scholar \\ 
National Merit Scholarship recipient \\ 
Dean's List, 1992 -- 1994 \\
National Dean's List, 1992 -- 1994 

\vspace*{0.2in}
\underline{\bf TEACHING EXPERIENCE:} ~\\
CS152, University of New Mexico, 2004 -- 2005

\vspace*{0.2in}
\underline{\bf DISSERTATION ADVISER:} ~\\ 
Professor Greg Heileman, University of New Mexico, Albuquerque, NM.

\vspace*{0.2in}
\underline{\bf RECENT COLLABORATORS:} ~\\
Greg Heileman, University of New Mexico \\
Pramod Jamkhedkar, University of New Mexico \\
Ravi Kadaboina, University of New Mexico \\
Chaouki Abdallah, University of New Mexico \\
Bob Ballance, Sandia National Laboratories

\end{document}
    
