\documentclass [11pt]{article}
%\nofiles

\pagestyle{plain}

\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}

%%%%%%%%%% EXACT 1in MARGINS %%%%%%% 
\setlength{\textwidth}{6.5in}     
\setlength{\oddsidemargin}{0in}   
\setlength{\evensidemargin}{0in}  
\setlength{\textheight}{8.5in}   
\setlength{\topmargin}{0in}    
\setlength{\headheight}{0in}    
\setlength{\headsep}{0in}         
\setlength{\footskip}{.5in}   

\begin{document}
%%%%%%%%% BIOGRAPHICAL SKETCH -- 2 pages/PI
\setlength{\baselineskip}{12pt}
\newpage
\setcounter{page}{1}
\parindent 0in
\begin{center}
{\Large\bf{\sc Biographical Sketch}}
\end{center}
\vspace*{-0.1in}
{\textcolor{black}{\makebox[6.5in]{\hrulefill}} ~\\
\vspace*{-0.35in}
\begin{tabbing}
   {\bf NAME} \hspace*{2.5in} \= {\bf POSITION TITLE} \\
   Gregory L. Heileman	      \>  Professor \& Assoc. Chair, ECE Department, \\
                                                     \> University of New Mexico
\end{tabbing}
\vspace*{-0.1in}
{\textcolor{black}{\makebox[6.5in]{\hrulefill}} ~\\
\vspace*{-0.2in}
\underline{\bf EMPLOYMENT:} ~\\
\begin{itemize}
\item August 2004 -- present: Associate Chair \& Director of Undergraduate Programs, Department of Electrical and Computer Engineering, University of New Mexico, Albuquerque, NM.
\item June 2002 -- present: Professor, Department of Electrical and Computer Engineering, University of New Mexico, Albuquerque, NM.
\item June 1996 -- June 2002: Associate Professor, Department of Electrical and Computer Engineering, University of New Mexico, Albuquerque, NM.
\item August 1990 -- June 1996:  Assistant Professor, Department of Electrical and Computer Engineering, University of New Mexico, Albuquerque, NM.
\item August 1989 -- August 1990: Visiting Assistant Professor, Department of Computer Engineering, University of Central Florida, Orlando, FL.
\end{itemize}
\vspace*{-0.1in}
{\textcolor{black}{\makebox[6.5in]{\hrulefill}} ~\\

\vspace*{-0.2in}
\underline{\bf EDUCATION:} ~\\
\begin{tabular}{lccc}
{\bf INSTITUTION}  & {\bf DEGREE} & {\bf YEAR} & {\bf  FIELD OF} \\ 
                                                     &&{\bf CONFERRED} & {\bf STUDY} \\
Univ. of Central Florida & Ph.D. & 1989 & Computer Engineering \\
Univ. North Carolina, Chapel Hill & M.S. & 1986 & Biomedical Eng. \& Mathematics \\
Wake Forest Univ. & B.S.	& 1982  & Biology \\~\\
\end{tabular}

{\textcolor{black}{\makebox[6.5in]{\hrulefill}} ~\\
\underline{\bf MEMBERSHIP:} ~\\ 
IEEE (Senior Member)

{\textcolor{black}{\makebox[6.5in]{\hrulefill}} ~\\
%\vspace*{-0.2in}
{\bf A. \  \ \underline{FIVE SELECTED RELEVANT PUBLICATIONS:}}
\begin{enumerate}
\item P.~A. Jamkhedkar and G.~L. Heileman. Digital Rights Management Architectures. 
{\sl Computers \& Electrical Engineering, Special Issue: Circuits and Systems for Real-Time Security and Copyright Protection of Multimedia}, Elsevier Press, Aug. 16, 2008. ~\\
http://dx.doi.org/10.1016/j.compeleceng.2008.06.012

\item
P.~A. Jamkhedkar and G.~L. Heileman.  A Formal Conceptual Model for Rights.  {\sl Proceedings of the Eighth ACM Workshop on Digital Rights Management}, Alexandria, VA, pp. 29--38, Oct. 27, 2008. 

\item S. Al-Saffar and G.~L. Heileman. Semantic Impact Graphs for Information Valuation. {\sl Proceeding of the Eighth ACM Symposium on Document Engineering}, Sao Paulo, Brazil, pp. 209--212, Sept. 16--19, 2008.

\item S. Al-Saffar and G.~L. Heileman. Semantics-Based Information Valuation. {\sl Proceedings of the 4-th IEEE International Conference on Intelligent Systems IS'08}, Varna, Bulgaria, Vol. 1, pp. 6-51--6-58, Sept. 6--8, 2008.

\item S. Al-Saffar and G.~L. Heileman. Experimental Bounds on the Usefulness of Personalized and Topic PageRank. {\sl IEEE/WIC/ACM International Conference on Web Intelligence},
 Silicon Valley, USA, pp. 671--675, Nov 2--5, 2007.
 \end{enumerate} 

{\textcolor{black}{\makebox[6.5in]{\hrulefill}} ~\\
%\vspace*{-0.2in}
{\bf B. \  \ \underline{OTHER PUBLICATIONS:}} 
\begin{enumerate}
\item T.-T. Quach F. P\'erez-Gonz\'alez and G.~L. Heileman. Model-Based Steganalysis Using Invariant Features. 
IS\&T/SPIE Electronic Imaging Science and Technology: Media Forensics and Security XI~(Conference EI120), San Jose, CA, Jan. 18--22, 2009 (to appear).
\item P.~A. Jamkhedkar and G.~L. Heileman.  Rights Expression Languages, in S. Lian and Y. Zhang (Editors), editor, {Handbook of Research on Secure Multimedia Distribution}, IGI Global, Hershey, PA, 2008. 
\item  A.~R. Franco, J. Ling, A. Caprihan, V.~D. Calhoun, R. Jung, G.~L. Heileman and A.~R. Mayer. Multimodal and Multi-tissue Measures of Connectivity Revealed by Joint Independent Component Analysis, {\sl IEEE Journal of Selected Topics in Signal Processing, Special Issue on fMRI Analysis for Human Brain Mapping}, 2(6), 2008. 
 \item
G.~L. Heileman, P.~A. Jamkhedkar, J. Khoury and C. Hrncir. The DRM Game.  {\sl Proceedings of the Seventh ACM Workshop on Digital Rights Management}, Alexandria, VA,  pp. 54--62 Oct. 29, 2007.
\item
M. Mart\'inez-Ram\'on, V. Koltchinskii, G.~L. Heileman, and S. Posse. fMRI pattern
classification using neuroanatomically constrained boosting. {\sl Neuroimage},
31(3):1129--1141, July 2006.
\end{enumerate}

{\textcolor{black}{\makebox[6.5in]{\hrulefill}} ~\\
\underline{\bf CURRENT STUDENTS:} ~\\
PhD: Sinan Al-Saffar,  Alexandre Franco, Pramod Jamkhedkar, Tu-Thach Ong, Craig Vineyard ~\\
MS: Matthew Bonshak

\vspace*{0.1in}
\underline{\bf PREVIOUS PhD STUDENTS:} ~\\ 
James Howse, Wenbin Luo, Bradley Smith, Steven Verzi, Henry Jerez

\vspace*{0.2in}
\underline{\bf DISSERTATION ADVISER:} ~\\ 
Professor Michael Georgiopoulos, University of Central Florida, Orlando, FL.

\vspace*{0.2in}
\underline{\bf RECENT COLLABORATORS:} ~\\
Dr. C.T. Abdallah, University of New Mexico; Dr. H.N. Jerez, Microsoft; Dr. R.E. Kahn, Corporation for National Research Initiatives;  Dr. M. Georgiopoulos, University of Central Florida; Dr. T.P. Hill, Cal Poly, San Luis Obispo; Dr. B. Horne, Trusted Systems Lab, Hewlett-Packard; Dr. V. Koltchinskii, Georgia Institute of Technology; Dr. M. Mart\'inez-Ram\'on, Universidad Carlos III de Madrid; Dr. F. P\'erez-Gonz\'alez, Universidad de Vigo; Dr. W.W. Shu, University of New Mexico;  Dr. S.J. Verzi, Sandia National Laboratories.

\end{document}
    
